A Triple Origin for Twin Blue Stragglers in Compact Binaries

### 2018-12-10 BSS7782.tex
updated text file, renamed files, and added makefile

\begin{figure}[ht!]
  \includegraphics[width=\columnwidth]{fig_MvsTime_N80k_M012R100RSun1109MSun_a02au.pdf}
\caption{Evolution of the masses (normalized to those at the moment of
  Roche-lobe overflow) of each of the three stars as a function of
  time for the first 1000\,days. (see Fig.\.\ref{fig:topview_at_t0}
  for a face-on representation of the initial conditions and
  fig.\,\ref{fig:topview_at_t1000day} for the final conditions}.  The
green and orange dashed curves give the masses of the inner two stars,
whereas the solid blue curve is the mass of the outer most star.
\label{fig:mass_evolution_for_M1.2M1.1M0.9a02e00i09}
\end{figure}

@@

\input /home/spz/Latex/lib/bib/references

%\bibliographystyle{/home/spz/Latex/lib/styles/elsevier/elsarticle-num} 
%\bibliography{references}

>>>>

\begin{figure}[ht!]
  \includegraphics[width=\columnwidth]{fig_MvsTime_N80k_M012R100RSun1109MSun_a02au.pdf}
\caption{Evolution of the masses (normalized to those at the moment of
  Roche-lobe overflow) of each of the three stars as a function of
  time for the first 1000\,days. (see Fig.\,\ref{fig:topview_at_t0}
  for a face-on representation of the initial conditions and
  fig.\,\ref{fig:topview_at_t1000day} for the final conditions}.  The
green and orange dashed curves give the masses of the inner two stars,
whereas the solid blue curve is the mass of the outer most star.
\label{fig:mass_evolution_for_M1.2M1.1M0.9a02e00i09}
\end{figure}

@@

\bibliographystyle{apj}
\bibliography{BBS7782}

%\input /home/spz/Latex/lib/bib/references
%\bibliographystyle{/home/spz/Latex/lib/styles/elsevier/elsarticle-num} 
%\bibliography{references}
